`r spec$datasetname`

### 2025-06-20 report/index.qmd
typos

---
title: "Liste des publications"
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    number-depth: 2
    other-links:
      - text: Document de travail
        icon: newspaper
        href: https://aqlt.github.io/publishTC.wp/Article.html
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
      - text: Package {publishTC}
        icon: box
        href: https://github.com/AQLT/publishTC
date: today
date-format: long
params:
  file: "../data/IPI.yml"
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
lang: fr
language:
 title-block-author-single: Auteur
---

>>>>

---
title: "Liste des publications"
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    number-depth: 2
    other-links:
      - text: Document de travail
        icon: newspaper
        href: https://aqlt.github.io/publishTC.wp/article.html
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
      - text: Package {publishTC}
        icon: box
        href: https://github.com/AQLT/publishTC
date: today
date-format: long
params:
  file: "../data/IPI.yml"
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
lang: fr
language:
 title-block-author-single: Auteur
---

### 2025-06-20 report/template.qmd
typos

---
format: 
  html:
    toc: true
    fig-format: png
    number-sections: true
    embed-resources: true
    number-depth: 2
    other-links:
      - text: Autres publications
        icon: patch-plus
        href: https://aqlt.github.io/publishTC.wp/
      - text: Document de travail
        icon: newspaper
        href: https://aqlt.github.io/publishTC.wp/Article.html
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
      - text: Package {publishTC}
        icon: box
        href: https://github.com/AQLT/publishTC
date: today
date-format: long
params:
  file: "../data/IPI.yml"
# execute:
#   cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
lang: fr
echo: false
eval: true
fig-height: 6
fig-width: 8
language:
 title-block-author-single: Auteur
---

>>>>

---
format: 
  html:
    toc: true
    fig-format: png
    number-sections: true
    embed-resources: true
    number-depth: 2
    other-links:
      - text: Autres publications
        icon: patch-plus
        href: https://aqlt.github.io/publishTC.wp/
      - text: Document de travail
        icon: newspaper
        href: https://aqlt.github.io/publishTC.wp/article.html
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
      - text: Package {publishTC}
        icon: box
        href: https://github.com/AQLT/publishTC
date: today
date-format: long
params:
  file: "../data/IPI.yml"
# execute:
#   cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
lang: fr
echo: false
eval: true
fig-height: 6
fig-width: 8
language:
 title-block-author-single: Auteur
---
